Appendix for "Navigating Hostility: The Effect of Nonprofit Transparency and Accountability on Donor Preferences in the Face of Shrinking Civic Space

### 2025-04-15 manuscript/appendix.qmd
Final edits pre-final submission

---
title: 'Appendix for "Navigating Hostility: The Effect of Nonprofit Transparency and Accountability on Donor Preferences in the Face of Shrinking Civic Space"'
short-title: 'Appendix for "Navigating Hostility"'
date: "2025-01-22"
author:
- name: Suparna Chaudhry
  affiliation: Lewis and Clark College
  url: http://www.suparnachaudhry.com/
  email: schaudhry@lclark.edu
  orcid: 0000-0003-3506-7590
- name: Marc Dotson
  affiliation: Utah State University
  url: https://occasionaldivergences.com/
  email: marc.dotson@usu.edu
  orcid: 0000-0001-7846-3660
- name: Andrew Heiss
  affiliations: 
    - id: gsu
      name: Georgia State University
      department: Andrew Young School of Policy Studies, Department of Public Management and Policy
      address: "55 Park Place NE, #464"
      city: Atlanta
      region: GA
      country: USA
      postal-code: 30303
  url: https://www.andrewheiss.com/
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
  attributes:
    corresponding: true
code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/silent-skywalk>"
bibliography: references.bib
csl: csl/apa.csl
link-citations: true
crossref: 
  tbl-title: "Table&nbsp;A"
  fig-title: "Figure&nbsp;A"
toc: true
format: 
  html: default
  hikmah-pdf:
    include-in-header: 
      - tex/tbl-fig-to-toc.tex
  hikmah-manuscript-pdf+ms:
    include-in-header: 
      - tex/tbl-fig-to-toc.tex
---

@@

tar_load(c(
  participant_summary, model_summary_table, feature_lookup, level_lookup, cps_diffs
))

@@

@@

tbl_participant_summary$Demographics %>% 
  select(-category, -Question) %>% 
  tt(width = c(0.6, 0.15, 0.15)) %>%
  group_tt(j = list("Demographics" = 1:3)) %>%
  group_tt(
    i = tbl_participant_summary$Demographics$Question, 
    indent = 1
  ) %>%
  style_tt(i = -1, align = "c", bold = TRUE) %>%
  style_tt(j = 1, align = "l") %>%
  style_tt(j = 2:3, align = "c") %>%
  style_tt(
    i = get_row_group_index(tbl_participant_summary$Demographics$Question),
    line = "b", line_width = 0.05, align = "l", bold = TRUE
  ) %>%
  style_tt(
    bootstrap_class = "table table-sm",
    tabularray_inner = inner
  ) %>%
  format_tt(escape = TRUE)
```

@@

tbl_participant_summary$`Attitudes toward charity` %>% 
  select(-category, -Question) %>% 
  tt(width = c(0.6, 0.15, 0.15)) %>%
  group_tt(j = list("Attitudes toward charity" = 1:3)) %>%
  group_tt(
    i = tbl_participant_summary$`Attitudes toward charity`$Question, 
    indent = 1
  ) %>%
  style_tt(i = -1, align = "c", bold = TRUE) %>%
  style_tt(j = 1, align = "l") %>%
  style_tt(j = 2:3, align = "c") %>%
  style_tt(
    i = get_row_group_index(tbl_participant_summary$`Attitudes toward charity`$Question),
    line = "b", line_width = 0.05, align = "l", bold = TRUE
  ) %>%
  style_tt(
    bootstrap_class = "table table-sm",
    tabularray_inner = inner
  ) %>%
  format_tt(escape = TRUE)
```

@@

tbl_participant_summary$`Politics, ideology, and religion` %>% 
  select(-category, -Question) %>%
  tt(width = c(0.6, 0.15, 0.15)) %>%
  group_tt(j = list("Politics, ideology, and religion" = 1:3)) %>%
  group_tt(
    i = tbl_participant_summary$`Politics, ideology, and religion`$Question,
    indent = 1
  ) %>%
  style_tt(i = -1, align = "c", bold = TRUE) %>%
  style_tt(j = 1, align = "l") %>%
  style_tt(j = 2:3, align = "c") %>%
  style_tt(
    i = get_row_group_index(tbl_participant_summary$`Politics, ideology, and religion`$Question),
    line = "b", line_width = 0.05, align = "l", bold = TRUE
  ) %>%
  style_tt(
    bootstrap_class = "table table-sm",
    tabularray_inner = inner
  ) %>%
  format_tt(escape = TRUE)
```

@@

To find the causal effects defined in each of our estimands, we calculate EMMs by finding the fitted probability-scale values for each cell in a balanced reference grid of all 576 possible combinations of feature levels (2 transparency × 2 accountability × 3 government relationships × 4 organizations × 4 issues × 3 funding = 576 rows). We then calculate group averages and contrasts in group averages for each of the features of interest, marginalizing over all other features.

@@

```{r}
#| label: tbl-coefs-orig
#| tbl-cap: Original multinomial logistic regression model coefficients
#| include: true
notes <- c(
  "Estimates are median posterior log odds from a multinomial logistic regression model with three possible categories, and the columns for µ1, µ2, and µ3 represent estimates for each of the outcomes;",
  "95% credible intervals (equal-tailed quantile intervals) in brackets."
)

@@

To convert EMMs and AMCEs to a more interpretable probability scale (rather than the original log odds scale), we generate predicted values (marginalized across the three µ terms) for each of the 576 unique combinations of feature levels. @tbl-grid-example provides an excerpt from this grid, showing six rows where accountability, organization, issue area, and funding are identical and held constant, while transparency and government relations vary.

@@

notes <- list(
  `*` = list(i = 0, j = c(2, 4), text = tt_md("Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.")),
  `†` = list(i = 0, j = 5, text = tt_md("The probability of direction (*p*~direction~) is the probability that the posterior AMCE is strictly positive or negative—it is the proportion of the posterior AMCE that is the sign of the median."))
)

@@

notes <- list(
  `*` = list(i = 0, j = 2, text = tt_md("Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets."))
)

@@

This is an anonymized and condensed version of our full OSF preregistration protocol.
:::

>>>>

---
title: 'Appendix for "Navigating Hostility: The Effect of Nonprofit Transparency and Accountability on Donor Preferences in the Face of Shrinking Civic Space"'
short-title: 'Appendix for "Navigating Hostility"'
date: "2025-04-14"
author:
- name: Suparna Chaudhry
  affiliation: Lewis and Clark College
  url: http://www.suparnachaudhry.com/
  email: schaudhry@lclark.edu
  orcid: 0000-0003-3506-7590
- name: Marc Dotson
  affiliation: Utah State University
  url: https://occasionaldivergences.com/
  email: marc.dotson@usu.edu
  orcid: 0000-0001-7846-3660
- name: Andrew Heiss
  affiliations: 
    - id: gsu
      name: Georgia State University
      department: Andrew Young School of Policy Studies, Department of Public Management and Policy
      address: "55 Park Place NE, #464"
      city: Atlanta
      region: GA
      country: USA
      postal-code: 30303
  url: https://www.andrewheiss.com/
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
  attributes:
    corresponding: true
code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/silent-skywalk>"
bibliography: references.bib
csl: csl/apa.csl
link-citations: true
crossref: 
  tbl-title: "Table&nbsp;A"
  fig-title: "Figure&nbsp;A"
toc: true
format: 
  html: default
  hikmah-pdf:
    include-in-header: 
      - tex/tbl-fig-to-toc.tex
  hikmah-manuscript-pdf+ms:
    include-in-header: 
      - tex/tbl-fig-to-toc.tex
---

@@

tar_load(c(
  participant_summary, model_summary_table, feature_lookup, level_lookup, 
  cps_diffs, data_sans_conjoint
))

details <- list(
  n = nrow(data_sans_conjoint),
  n_nice = label_comma()(nrow(data_sans_conjoint)),
  combos = 2 * 2 * 3 * 4 * 4 * 3
)

@@

summary_notes <- list(
  `*` = list(i = 0, j = 2, text = tt_md(paste0("N = ", details$n_nice, " respondents.")))
)

@@

tbl_participant_summary$Demographics %>% 
  select(-category, -Question) %>% 
  tt(width = c(0.6, 0.15, 0.15), notes = summary_notes) %>%
  group_tt(j = list("Demographics" = 1:3)) %>%
  group_tt(
    i = tbl_participant_summary$Demographics$Question, 
    indent = 1
  ) %>%
  style_tt(i = -1, align = "c", bold = TRUE) %>%
  style_tt(j = 1, align = "l") %>%
  style_tt(j = 2:3, align = "c") %>%
  style_tt(
    i = get_row_group_index(tbl_participant_summary$Demographics$Question),
    line = "b", line_width = 0.05, align = "l", bold = TRUE
  ) %>%
  style_tt(
    bootstrap_class = "table table-sm",
    tabularray_inner = inner
  ) %>%
  format_tt(escape = TRUE)
```

@@

tbl_participant_summary$`Attitudes toward charity` %>% 
  select(-category, -Question) %>% 
  tt(width = c(0.6, 0.15, 0.15), notes = summary_notes) %>%
  group_tt(j = list("Attitudes toward charity" = 1:3)) %>%
  group_tt(
    i = tbl_participant_summary$`Attitudes toward charity`$Question, 
    indent = 1
  ) %>%
  style_tt(i = -1, align = "c", bold = TRUE) %>%
  style_tt(j = 1, align = "l") %>%
  style_tt(j = 2:3, align = "c") %>%
  style_tt(
    i = get_row_group_index(tbl_participant_summary$`Attitudes toward charity`$Question),
    line = "b", line_width = 0.05, align = "l", bold = TRUE
  ) %>%
  style_tt(
    bootstrap_class = "table table-sm",
    tabularray_inner = inner
  ) %>%
  format_tt(escape = TRUE)
```

@@

tbl_participant_summary$`Politics, ideology, and religion` %>% 
  select(-category, -Question) %>%
  tt(width = c(0.6, 0.15, 0.15), notes = summary_notes) %>%
  group_tt(j = list("Politics, ideology, and religion" = 1:3)) %>%
  group_tt(
    i = tbl_participant_summary$`Politics, ideology, and religion`$Question,
    indent = 1
  ) %>%
  style_tt(i = -1, align = "c", bold = TRUE) %>%
  style_tt(j = 1, align = "l") %>%
  style_tt(j = 2:3, align = "c") %>%
  style_tt(
    i = get_row_group_index(tbl_participant_summary$`Politics, ideology, and religion`$Question),
    line = "b", line_width = 0.05, align = "l", bold = TRUE
  ) %>%
  style_tt(
    bootstrap_class = "table table-sm",
    tabularray_inner = inner
  ) %>%
  format_tt(escape = TRUE)
```

@@

To find the causal effects defined in each of our estimands, we calculate EMMs by finding the fitted probability-scale values for each cell in a balanced reference grid of all `r details$combos` possible combinations of feature levels (2 transparency × 2 accountability × 3 government relationships × 4 organizations × 4 issues × 3 funding = `r details$combos` rows). We then calculate group averages and contrasts in group averages for each of the features of interest, marginalizing over all other features.

@@

```{r}
#| label: tbl-coefs-orig
#| tbl-cap: Original multinomial logistic regression model coefficients
#| include: true
notes <- c(
  paste0("N = ", details$n_nice, " respondents. Estimates are median posterior log odds from a multinomial logistic regression model with three possible categories, and the columns for µ1, µ2, and µ3 represent estimates for each of the outcomes;"),
  "95% credible intervals (equal-tailed quantile intervals) in brackets."
)

@@

To convert EMMs and AMCEs to a more interpretable probability scale (rather than the original log odds scale), we generate predicted values (marginalized across the three µ terms) for each of the `r details$combos` unique combinations of feature levels. @tbl-grid-example provides an excerpt from this grid, showing six rows where accountability, organization, issue area, and funding are identical and held constant, while transparency and government relations vary.

@@

notes <- list(
  `*` = list(i = 0, j = c(2, 4), text = tt_md(paste0("N = ", details$combos, " estimated marginal means collapsed into feature-specific means. Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets."))),
  `†` = list(i = 0, j = 5, text = tt_md("The probability of direction (*p*~direction~) is the probability that the posterior AMCE is strictly positive or negative—it is the proportion of the posterior AMCE that is the sign of the median."))
)

@@

notes <- list(
  `*` = list(i = 0, j = 2, text = tt_md(paste0("N = ", details$combos, " estimated marginal means collapsed into feature-specific means. Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.")))
)

@@

This is an anonymized and condensed version of our full OSF preregistration protocol, which is available at <https://doi.org/10.17605/OSF.IO/HSBYD>.
:::
